Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2019-01-22 AnalyticStructure_main.tex
update plot and supplementary

We have analyzed the fulfillment of Eq.~\eqref{sminus2} for molecules of various
sizes and symmetries.
In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
We notice that, in both the cases, a considerable number of pseudo-continuum excitations is required
to find the correct result; the sector of the discrete excitations
%, even though parametrized by localized, observable (in the sense of reproducible) excited states,
appears to be largely insufficient to express the reference fluctuation state. In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t. the one coming from the continuum sector.

% \begin{figure}
% \includegraphics[scale=0.6]{Fig6_CO_statPolvsExc.eps}
% \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,
% w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
% horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the
% oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
% \end{figure}

\begin{figure}
\centering
\subfloat[$CO$]
{\label{CO_alphavsExc}
\includegraphics[scale=0.6]{Fig6a_CO_statPolvsExc.eps}} \\
\centering
\subfloat[$C_{60}$]
{\label{C60_alphavsExc}
\includegraphics[scale=0.2]{Fig6b_C60_statPolvsExc.eps}}
\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,
w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the
oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
\end{figure}

>>>>

We have analyzed the fulfillment of Eq.~\eqref{sminus2} for molecules of various
sizes and symmetries.
In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
We notice that, in both the cases, a considerable number of pseudo-continuum excitations is required
to find the correct result; the sector of the discrete excitations appears to be largely insufficient to express the 
reference fluctuation state. 
%In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t. the one coming from the continuum sector.
In particular, in the case of $CO$, the complete excitation set is able to reproduce the reference value of $\alpha_{zz}$, but the contribution of localized sector is negligible w.r.t. the one coming from the continuum one. Instead, for the $C_{60}$, the localized sector provides a more significant contribution but a higher number of the psuedo-continuum excitations should be included in the sum of \eqref{sminus2} to satisfy the $S_{-2}$ sum-rule.

\begin{figure}
\centering
\subfloat[$CO$]
{\label{CO_alphavsExc}
\includegraphics[scale=0.6]{Fig6a_CO_statPolvsExc.eps}} \\
\centering
\subfloat[$C_{60}$]
{\label{C60_alphavsExc}
\includegraphics[scale=0.6]{Fig6b_C60_statPolvsExc.eps}}
\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,
w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the
oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
\end{figure}
